Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
hscc17

\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
and $a$ are the plant's coefficients, and $N$ and $M$ are the number of
poles and zeros for the corresponding block.

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.  Although there are several discretization methods available
in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
discretization is more suitable for representing the sampling and holding
processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is
equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
function $G(s)$ driven by ZOH).  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For convenience, we will use only the notation $G(z)$ to represent the pulse
transfer function.
%
\end{mylemma}

>>>>

%\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are vectors containing the controller's coefficients;  
similarly $b$ and $a$ encompas the plant's coefficients;  
and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.  Although there are several discretization methods available
in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
discretization is more suitable for representing the sampling and holding
processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is
equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
function $G(s)$ driven by ZOH).  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}
